---
title: "CMU Library"
output: 
  html_document:
    toc: true
    toc_depth: 4 
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(message=FALSE)
knitr::opts_chunk$set(warning=FALSE)
```

```{r library, include=FALSE}
library(ggplot2)
library(questionr)
library(plotly)
library(dplyr)
library(tm)
library(SnowballC)
library(tidytext)
```

```{r data, include=FALSE}
mydata <- read.csv("~/Desktop/Research/20200512_SURA_library-usage.csv",TRUE,",", na.strings=c("","NA"), stringsAsFactors = FALSE)
class(mydata)

newdata <- mydata %>% mutate(New.Patron.Group = ifelse(mydata$Patron.Group == "Carnegie Mellon Faculty" | mydata$Patron.Group == "Qatar Faculty", "Faculty", 
      ifelse(mydata$Patron.Group == "Carnegie Mellon Staff", "Staff",
      ifelse(mydata$Patron.Group == "Carnegie Mellon Undergrads" | mydata$Patron.Group ==   
               "Carnegie Mellon Grad Students", "Student", "Other"))))
class(newdata)
newdata <- newdata %>% mutate(New.Publication.Date = ifelse(mydata$Begin.Publication.Date %in% 1800:1804, "1800-1804",
      ifelse(mydata$Begin.Publication.Date %in% 1805:1809,"1805-1809",
      ifelse(mydata$Begin.Publication.Date %in% 1810:1814,"1810-1814",
      ifelse(mydata$Begin.Publication.Date %in% 1815:1819,"1815-1819",
      ifelse(mydata$Begin.Publication.Date %in% 1820:1824,"1820-1824",
      ifelse(mydata$Begin.Publication.Date %in% 1825:1829,"1825-1829",
      ifelse(mydata$Begin.Publication.Date %in% 1830:1834,"1830-1834",
      ifelse(mydata$Begin.Publication.Date %in% 1835:1839,"1835-1839",
      ifelse(mydata$Begin.Publication.Date %in% 1840:1844,"1840-1844",
      ifelse(mydata$Begin.Publication.Date %in% 1845:1849,"1845-1849",
      ifelse(mydata$Begin.Publication.Date %in% 1850:1854,"1850-1854",
      ifelse(mydata$Begin.Publication.Date %in% 1855:1859,"1855-1859",
      ifelse(mydata$Begin.Publication.Date %in% 1860:1864,"1860-1864",
      ifelse(mydata$Begin.Publication.Date %in% 1865:1869,"1865-1869",
      ifelse(mydata$Begin.Publication.Date %in% 1870:1874,"1870-1874",
      ifelse(mydata$Begin.Publication.Date %in% 1875:1879,"1875-1879",
      ifelse(mydata$Begin.Publication.Date %in% 1880:1884,"1880-1884",
      ifelse(mydata$Begin.Publication.Date %in% 1885:1889,"1885-1889",
      ifelse(mydata$Begin.Publication.Date %in% 1890:1894,"1890-1894",
      ifelse(mydata$Begin.Publication.Date %in% 1895:1899,"1895-1899",
      ifelse(mydata$Begin.Publication.Date %in% 1900:1904,"1900-1904",
      ifelse(mydata$Begin.Publication.Date %in% 1905:1909,"1905-1909",
      ifelse(mydata$Begin.Publication.Date %in% 1910:1914,"1910-1914",
      ifelse(mydata$Begin.Publication.Date %in% 1915:1919,"1915-1919",
      ifelse(mydata$Begin.Publication.Date %in% 1920:1924,"1920-1924",
      ifelse(mydata$Begin.Publication.Date %in% 1925:1929,"1925-1929",
      ifelse(mydata$Begin.Publication.Date %in% 1930:1934,"1930-1934",
      ifelse(mydata$Begin.Publication.Date %in% 1935:1939,"1935-1939",
      ifelse(mydata$Begin.Publication.Date %in% 1940:1944,"1940-1944",
      ifelse(mydata$Begin.Publication.Date %in% 1945:1949,"1945-1949",
      ifelse(mydata$Begin.Publication.Date %in% 1950:1954,"1950-1954",
      ifelse(mydata$Begin.Publication.Date %in% 1955:1959,"1955-1959",
      ifelse(mydata$Begin.Publication.Date %in% 1960:1964,"1960-1964",
      ifelse(mydata$Begin.Publication.Date %in% 1965:1969,"1965-1969",
      ifelse(mydata$Begin.Publication.Date %in% 1970:1974,"1970-1974",
      ifelse(mydata$Begin.Publication.Date %in% 1975:1979,"1975-1979",
      ifelse(mydata$Begin.Publication.Date %in% 1980:1984,"1980-1984",
      ifelse(mydata$Begin.Publication.Date %in% 1985:1989,"1985-1989",
      ifelse(mydata$Begin.Publication.Date %in% 1990:1994,"1990-1994",
      ifelse(mydata$Begin.Publication.Date %in% 1995:1999,"1995-1999",
      ifelse(mydata$Begin.Publication.Date %in% 2000:2004,"2000-2004",
      ifelse(mydata$Begin.Publication.Date %in% 2005:2009,"2005-2009",
      ifelse(mydata$Begin.Publication.Date %in% 2010:2014,"2010-2014",
      ifelse(mydata$Begin.Publication.Date %in% 2015:2019,"2015-2019",
      ifelse(mydata$Begin.Publication.Date %in% 2020:2024,"2020-2024", 
             "NA"))))))))))))))))))))))))))))))))))))))))))))))

newdata <- newdata %>% mutate(Book.Age = ifelse(newdata$New.Publication.Date == "NA", "NA", 2020-as.numeric(newdata$Begin.Publication.Date)))

newdata <- newdata %>% mutate(Book.Age.SqrtTransform = ifelse(newdata$Book.Age == "NA", "NA", sqrt(as.numeric(newdata$Book.Age))))

newdata <- newdata %>% mutate(Loan.Month.Number = format (as.Date(mydata$Loan.Date), "%m"))

newdata <- newdata %>% mutate(Loan.Month.Eng = ifelse(newdata$Loan.Month.Number == "01", "January", 
      ifelse(newdata$Loan.Month.Number == "02", "February", 
      ifelse(newdata$Loan.Month.Number == "03", "March", 
      ifelse(newdata$Loan.Month.Number == "04", "April", 
      ifelse(newdata$Loan.Month.Number == "05", "May", 
      ifelse(newdata$Loan.Month.Number == "06", "June", 
      ifelse(newdata$Loan.Month.Number == "07", "July", 
      ifelse(newdata$Loan.Month.Number == "08", "August", 
      ifelse(newdata$Loan.Month.Number == "09", "September", 
      ifelse(newdata$Loan.Month.Number == "10", "October", 
      ifelse(newdata$Loan.Month.Number == "11", "November", "December"))))))))))))

newdata <- newdata %>% mutate(Return.Month.Number = format (as.Date(mydata$Return.Date), "%m"))

newdata <- newdata %>% mutate(Return.Month.Eng = ifelse(newdata$Return.Month.Number == "01", "January", 
      ifelse(newdata$Return.Month.Number == "02", "February", 
      ifelse(newdata$Return.Month.Number == "03", "March", 
      ifelse(newdata$Return.Month.Number == "04", "April", 
      ifelse(newdata$Return.Month.Number == "05", "May", 
      ifelse(newdata$Return.Month.Number == "06", "June", 
      ifelse(newdata$Return.Month.Number == "07", "July", 
      ifelse(newdata$Return.Month.Number == "08", "August", 
      ifelse(newdata$Return.Month.Number == "09", "September", 
      ifelse(newdata$Return.Month.Number == "10", "October", 
      ifelse(newdata$Return.Month.Number == "11", "November",
      ifelse(newdata$Return.Month.Number == "12", "December", "NA")))))))))))))

newdata <- newdata %>% mutate(Loan.Hour = format(strptime(newdata$Loan.Time,"%H:%M:%S"),'%H'))

newdata <- newdata %>% mutate(Loan.Hour.Read = ifelse(newdata$Loan.Hour == "00", "12AM", 
      ifelse(newdata$Loan.Hour == "01", "1AM", 
      ifelse(newdata$Loan.Hour == "02", "2AM", 
      ifelse(newdata$Loan.Hour == "03", "3AM", 
      ifelse(newdata$Loan.Hour == "04", "4AM", 
      ifelse(newdata$Loan.Hour == "05", "5AM", 
      ifelse(newdata$Loan.Hour == "06", "6AM", 
      ifelse(newdata$Loan.Hour == "07", "7AM", 
      ifelse(newdata$Loan.Hour == "08", "8AM", 
      ifelse(newdata$Loan.Hour == "09", "9AM", 
      ifelse(newdata$Loan.Hour == "10", "10AM",
      ifelse(newdata$Loan.Hour == "11", "11AM",
      ifelse(newdata$Loan.Hour == "12", "12PM", 
      ifelse(newdata$Loan.Hour == "13", "1PM", 
      ifelse(newdata$Loan.Hour == "14", "2PM", 
      ifelse(newdata$Loan.Hour == "15", "3PM", 
      ifelse(newdata$Loan.Hour == "16", "4PM", 
      ifelse(newdata$Loan.Hour == "17", "5PM", 
      ifelse(newdata$Loan.Hour == "18", "6PM", 
      ifelse(newdata$Loan.Hour == "19", "7PM", 
      ifelse(newdata$Loan.Hour == "20", "8PM", 
      ifelse(newdata$Loan.Hour == "21", "9PM",
      ifelse(newdata$Loan.Hour == "22", "10PM", "11PM"))))))))))))))))))))))))

newdata <- newdata %>% mutate(Loan.Days.LogTransform = log(Loan.Days+1))

CMUFacultyData <- filter(newdata, newdata$New.Patron.Group == "Faculty")

CMUStaffData <- filter(newdata, newdata$New.Patron.Group == "Staff")

CMUStudentData <- filter(newdata, newdata$New.Patron.Group == "Student")

otherPatronGroup <- filter(newdata, newdata$New.Patron.Group == "Other")    
```

## Introduction

## Exploratory Data Analysis

### Quantitative Variables  

#### *Loan Days*
###### Summary Statistics:
```{r loanDaySummary, include=FALSE}
mean(mydata[["Loan.Days"]])
median(mydata[["Loan.Days"]])
sd(mydata[["Loan.Days"]]) #Data is very spread out
max(mydata[["Loan.Days"]])
min(mydata[["Loan.Days"]])
```
```
1) Median: 2  
2) Standard Deviation: 71.78  
3) Maximum: 739  
4) Minimum: -26  
5) Mean: 38.47
```
###### Histogram:
```{r loanDayHistogram, echo=FALSE}
p <- ggplot(data = newdata, aes(x = Loan.Days.LogTransform)) + geom_histogram(fill = "lightblue3", color = "lightblue3") + theme_minimal() + labs(x = "Loan Days", y = "Frequency", title = "Frequency of Loan Days (After Log Transformation)") + theme(axis.title.y = element_text(size = 8), axis.title.x = element_text(size = 8), title = element_text(size = 9))

ggplotly(p)
```


#### *Loan Month*
###### Frequency Table:
```{r loanMonthFreqTable, echo=FALSE}
freq(newdata$Loan.Month.Eng, sort = "dec", total = TRUE)
```
###### Bar Graph:
```{r loanMonthBarChart, echo=FALSE}
newdata$Loan.Month.Eng <- factor(newdata$Loan.Month.Eng,levels = c("January", "February", "March", "April", "May", "June", "July", "August", "September", "October", "November", "December"))

p <- ggplot(data = newdata, aes(x = Loan.Month.Eng)) + geom_bar(fill = "lightblue3", color = "lightblue3") + theme_minimal() + labs(x = "Loan Month", y = "Frequency", title = "Frequency of Loan Month") + theme(axis.title.y = element_text(size = 8), axis.title.x = element_text(size = 8), title = element_text(size = 9), axis.text.x = element_text(size = 6, angle = 90))

ggplotly(p)
```

#### *Return Month*
```{r returnMonthFreqTable, echo=FALSE}
freq(newdata$Return.Month.Eng, sort = "dec", total = TRUE)
```
###### Bar Graph and Distribution Shape:
```{r returnDateBarChart, echo=FALSE}
newdata$Return.Month.Eng <- factor(newdata$Return.Month.Eng, levels = c("January", "February", "March", "April", "May", "June", "July", "August", "September", "October", "November", "December", ""))

p <- ggplot(data = newdata, aes(x = Return.Month.Eng)) + geom_bar(fill = "lightblue3", color = "lightblue3") + theme_minimal() + labs(x = "Return Month", y = "Frequency", title = "Frequency of Return Month") + theme(axis.title.y = element_text(size = 8), axis.title.x = element_text(size = 8), title = element_text(size = 9), axis.text.x = element_text(size = 6, angle = 90))

ggplotly(p)
```

#### *Loan Hour*
```{r loanHourFreqTable, echo=FALSE}
freq(newdata$Loan.Hour.Read, sort = "dec", total = TRUE)
```
###### Bar Graph and Distribution Shape:
```{r loanHourBarChart, echo=FALSE}
newdata$Loan.Hour.Read <- factor(newdata$Loan.Hour.Read, levels = c("12AM", "1AM", "2AM", "3AM", "4AM", "5AM", "6AM", "7AM", "8AM", "9AM", "10AM", "11AM", "12PM", "1PM", "2PM", "3PM", "4PM", "5PM", "6PM", "7PM", "8PM", "9PM", "10PM", "11PM"))

p <- ggplot(data = newdata, aes(x = Loan.Hour.Read)) + geom_bar(fill = "lightblue3", color = "lightblue3") + theme_minimal() + labs(x = "Loan Hour", y = "Frequency", title = "Frequency of Loan Hour") + theme(axis.title.y = element_text(size = 8), axis.title.x = element_text(size = 8), title = element_text(size = 9), axis.text.x = element_text(size = 6, angle = 90))

ggplotly(p)
```
  
### Categorical Variables  

#### *Patron Group*
###### Frequency Table:
```{r patronGroupFreqTable, echo=FALSE}
freq(mydata$Patron.Group, sort = "dec", total = TRUE)
```
###### Bar Graph:
```{r patronGroupBarGraph, echo=FALSE}
p <- ggplot(data = mydata, aes(x = Patron.Group)) + geom_bar(fill = "lightblue3", color = "lightblue3") + theme_minimal() + labs(x = "Patron Group", y = "Number of Items Loaned", title = "Number of Items Loaned by Patron Group") + theme(axis.text.x = element_text(size = 6, angle = 90), axis.title.y = element_text(size = 8), axis.title.x = element_text(size = 8), title = element_text(size = 9))

ggplotly(p)
```

#### *Academic Standing*
###### Frequency Table:
```{r academicStandingFreqTable, echo=FALSE}
academicTable <- filter(mydata, mydata$Statistical.Category.1 != "NA")

freq(academicTable$Statistical.Category.1, sort = "dec", total = TRUE)
```
###### Bar Graph:
```{r academicStandingBarChart, echo=FALSE}
p <- ggplot(data = academicTable, aes(x = Statistical.Category.1, fill = Statistical.Category.1)) + geom_bar() + theme_minimal() + labs(x = "Academic Standing", y = "Number of Items Loaned", title = "Number of Items Loaned by Academic Standing") + theme(axis.text.x = element_text(size = 6, angle = 90), axis.title.y = element_text(size = 8), axis.title.x = element_text(size = 8), title = element_text(size = 9)) + scale_fill_discrete(name = "Academic Standing") + theme(legend.text = element_text(size = 6), legend.title = element_text(size = 8))

ggplotly(p)
```

#### *Material Type*
###### Frequency Table (Top 5):
```{r materialTypeFreqTable, echo=FALSE, eval=FALSE}
freq(mydata$Material.Type, sort = "dec", total = TRUE)
```
Material Type | n | % 
------------- | ------------- | ------------- 
Book | 45007 | 59.2
Equipment | 20409 | 26.8
Music Score | 2798 | 3.7
Other | 1832 | 2.4
Video Recording | 1793 | 2.4

###### Bar Graph:
```{r materialTypeBarChart, echo=FALSE}
p <- ggplot(data = mydata, aes(x = Material.Type)) + geom_bar(fill = "lightblue3", color = "lightblue3") + theme_minimal() + labs(x = "Material Type", y = "Frequency", title = "Frequency by Material Type") + theme(axis.text.x = element_text(size = 6, angle = 90), axis.title.y = element_text(size = 8), axis.title.x = element_text(size = 8), title = element_text(size = 9))

ggplotly(p)
```

#### *Subject*
###### Top 25 Most Common Words (Not in Order):
```{r wordCorpus, include=FALSE}
wordCorpus <- Corpus(VectorSource(newdata$Subjects))

wordCorpus <- tm_map(wordCorpus, content_transformer(tolower))

wordCorpus <- tm_map(wordCorpus, removeWords, stopwords("english"))

#wordCorpus <- tm_map(wordCorpus, stripWhitespace)

wordCorpus <- tm_map(wordCorpus, removeNumbers)

wordCorpus <- tm_map(wordCorpus, removePunctuation)

wordCorpus <- tm_map(wordCorpus, removeWords, c("etc", "stateshistory", "aspects", "york", "conditions", "modernth")) 

dtm <- TermDocumentMatrix(wordCorpus)
#as.matrix(dtm)
findFreqTerms(dtm,1120)
```
Words (Top 25)|               |               |               |
------------- | ------------- | ------------- | ------------- | -------------  
Architecture | Century | Fiction | American | States     
Art | Social | Theory | History | Works
Computer | Systems | English | Criticism | Literature
Motion | United | African | War | Government
Films | World | Music | Drama | Piano

#### *Language*
###### Frequency Table (Top 5, excluding NA):
```{r languageFreqTable, eval=FALSE, echo=FALSE}
freq(mydata$Language.Code, sort = "dec", total = TRUE)
```
Subject | n | % 
------------- | ------------- | ------------- 
eng | 71430 | 94.0
zxx | 997 | 1.3
ger | 599 | 0.8
fre | 452 | 0.6
spa| 330 | 0.4

###### Bar Graph:
```{r languageBarGraph, echo=FALSE}
p <- ggplot(data = mydata, aes(x = Language.Code)) + geom_bar(fill = "lightblue3", color = "lightblue3") + theme_minimal() + labs(x = "Language Code", y = "Frequency", title = "Frequency by Language") + theme(axis.text.x = element_text(size = 6, angle = 90), axis.title.y = element_text(size = 8), axis.title.x = element_text(size = 8), title = element_text(size = 9))

ggplotly(p)
```
###### Bar Graph Without English:
```{r languageBarGraphNoEng, echo=FALSE}
noEngData <- filter(mydata, mydata$Language.Code != "eng")

p <- ggplot(data = noEngData, aes(x = Language.Code)) + geom_bar(fill = "lightblue3", color = "lightblue3") + theme_minimal() + labs(x = "Language Code", y = "Frequency", title = "Frequency by Language (No English)") + theme(axis.text.x = element_text(size = 6, angle = 90), axis.title.y = element_text(size = 8), axis.title.x = element_text(size = 8), title = element_text(size = 9))

ggplotly(p)
```

#### *Library*
###### Frequency Table:
```{r libraryFreqTable, echo=FALSE}
freq(mydata$Library.Name, sort = "dec", total = TRUE)
```
###### Bar Graph:
```{r libraryBarGraph, echo=FALSE}
p <- ggplot(data = mydata, aes(x = Library.Name)) + geom_bar(fill = "lightblue3", color = "lightblue3") + theme_minimal() + labs(x = "Library", y = "Number of Items Loaned", title = "Number of Items Loaned by Library") + theme(axis.text.x = element_text(size = 6, angle = 90), axis.title.y = element_text(size = 8), axis.title.x = element_text(size = 8), title = element_text(size = 9))

ggplotly(p)
```

#### *Circulation Desk*
###### Frequency Table:
```{r circDeskFreqTable, echo=FALSE}
freq(mydata$Circ.Desk.Name, sort = "dec", total = TRUE)
```
###### Bar Graph:
```{r circDeskBarGraph, echo=FALSE}
p <- ggplot(data = mydata, aes(x = Circ.Desk.Name, fill = Library.Name)) + geom_bar() + theme_minimal() + labs(x = "Circulation Desk", y = "Number of Items Loaned", title = "Number of Items Loaned by Circulation Desk") + theme(axis.text.x = element_text(size = 6, angle = 90), axis.title.y = element_text(size = 8), axis.title.x = element_text(size = 8), title = element_text(size = 9)) + scale_fill_discrete(name = "Circulation") + theme(legend.text = element_text(size = 6), legend.title = element_text(size = 8))

ggplotly(p)
```

#### *Publisher*
###### Frequency Table (Top 15, excluding N/A):
```{r publisherFreqTable, eval=FALSE, echo=FALSE}
freq(mydata$Publisher, sort = "dec", total = TRUE)
```
Publisher | n | % 
------------- | ------------- | ------------- 
Cambridge University Press | 1655 | 2.2
Oxford University Press | 1585 | 2.1
Pearson | 1099 | 1.4
Routledge | 791 | 1.0
McGraw-Hill | 706 | 0.9
Wiley | 656 | 0.9
Springer | 618 | 0.8
MIT Press| 547 | 0.7
Princeton University Press | 503 | 0.7
Palgrave Macmillan | 459 | 0.6
Dramatists Play Service | 444 | 0.6
Yale University Press | 420 | 0.6
Prentice Hall | 378 | 0.5
Harvard University Press | 366 | 0.5
University of California Press | 354 | 0.5

#### *Location*
###### Frequency Table (Top 15):
```{r locationFreqTable, eval=FALSE, echo=FALSE}
freq(mydata$Location.Name, sort = "dec", total = TRUE)
```

Location | n | % 
------------- | ------------- | ------------- 
STACKS-2 | 18279 | 24.0
HL-CIRCDK | 13064 | 17.2
ESCIRCDESK | 10617 | 14.0
STACKS | 6852 | 9.0
STACKS-4 | 6483 | 8.5
OVRSZQ-4 | 5098 | 6.7
Borrowing Resource Sharing Requests | 2876 | 3.8
BY-REQUEST | 1876 | 2.5
VIDEO-2 | 1816 | 2.4
STACKS-3 | 1773 | 2.3
Q-STACKS | 1630 | 2.1
BND-JOUR-3 | 857 | 1.1
MUS-OFC-4 | 767 | 1.0
OVRSZQ-3 | 588 | 0.8
CIRCDESK | 382 | 0.5

#### *Publication Date*
###### Frequency Table (Top 5):
```{r PubDateFreqTable, echo=FALSE, include=FALSE}
dateTable <- filter(newdata, newdata$New.Publication.Date != "NA")

freq(dateTable$New.Publication.Date, sort = "dec", total = TRUE)
```
Time Period | n | % 
------------- | ------------- | ------------- 
2010-2014 | 16541	| 28.8
2015-2019 | 8769 | 15.3
2005-2009 | 7056 | 12.3
2000-2004 | 6912	| 12.0
1995-1999 | 4101 | 7.1

###### Bar Graph (Excluding NA):
```{r pubDateBarGraph, echo=FALSE}
p <- ggplot(data = dateTable, aes(x = New.Publication.Date)) + geom_bar(fill = "lightblue3", color = "lightblue3") + theme_minimal() + labs(x = "Publication Date", y = "Frequency", title = "Frequency of Publication Date") + theme(axis.title.y = element_text(size = 8), axis.title.x = element_text(size = 8), title = element_text(size = 9), axis.text.x = element_text(angle = 90, size = 5))

ggplotly(p)
```

## Faculty&Staff Data Analysis

### Quantitative Variables  

#### *Loan Days*
###### Summary Statistics:
```{r CMUFacultyLoanDaySummary,eval=FALSE, echo=FALSE}
mean(CMUFacultyData[["Loan.Days"]])
median(CMUFacultyData[["Loan.Days"]])
sd(CMUFacultyData[["Loan.Days"]])
max(CMUFacultyData[["Loan.Days"]])
min(CMUFacultyData[["Loan.Days"]])
"------------------"
mean(CMUStaffData[["Loan.Days"]])
median(CMUStaffData[["Loan.Days"]])
sd(CMUStaffData[["Loan.Days"]]) #Data is very spread out
max(CMUStaffData[["Loan.Days"]])
min(CMUStaffData[["Loan.Days"]])
```
Summary Statistics | Carnegie Mellon Staff | Carnegie Mellon Faculty
------------- | ------------- | ------------- 
Mean | 46.14 | 56.82
Median | 3 | 15
Standard Deviation | 82.71 | 94.17
Maximum | 690 | 728
Minimum | 0 | 0

###### Boxplots:
```{r CMUFacultyLoanDayBoxplot, echo=FALSE}
facultyAndStaffWithNAFiltered <- filter(newdata, newdata$New.Patron.Group == "Staff" | newdata$New.Patron.Group == "Faculty")

ggplot(data = facultyAndStaffWithNAFiltered, aes(x = Loan.Days.LogTransform, fill = New.Patron.Group)) + geom_boxplot() + theme_minimal() + labs(x = "log(Loan Days)", y = "Frequency", title = "Distribution of Loan Days") + theme(axis.text.x = element_text(size = 6), axis.title.y = element_text(size = 8), axis.title.x = element_text(size = 8), title = element_text(size = 9)) + scale_fill_discrete(name = "Patron Group") + theme(legend.text = element_text(size = 6), legend.title = element_text(size = 8))
```

###### Two Sample T-test:
Having summarized the variable, we now turn to the formal hypotheses, we will test if the mean of log transformation of loan days differs significantly for faculty vs. staff:  

$H0: μS-μF = 0$  
$Ha: μS-μF ≠ 0$  

(where $μS$ represent the true mean loan day of staff, and $μF$ represent the true mean loan day of faculty)   

```{r CMUFacultyLoanDayTtest, echo=FALSE}
t.test(Loan.Days.LogTransform~New.Patron.Group, data=facultyAndStaffWithNAFiltered)
```
Running a Two Sample t-test yields a test statistic of 11.799 and a p-value that's very close to zero. Since the p-value is less than the alpha significance level of 0.05, we reject the null hypothesis and hence **find evidence of a relationship** between average loan days and patron group.   

#### *Loan Month*
###### Loan Month Ranking (Most frequent to least):
```{r facultyLoanMonthFreqTable, eval=FALSE, echo=FALSE}
freq(CMUFacultyData$Loan.Month.Eng, sort = "dec", total = TRUE)

freq(CMUStaffData$Loan.Month.Eng, sort = "dec", total = TRUE)
```
Ranking of Loan Month | Carnegie Mellon Staff | Carnegie Mellon Faculty
------------- | ------------- | ------------- 
 1  | July | January
 2  | October | September
 3  | February | April
 4  | September | October
 5  | April | August
 6  | January | February
 7  | March | June
 8  | May | March
 9  | November | May
 10 | August | July
 11 | June | November
 12 | December | December

###### Bar Graph:
```{r facultyLoanMonthBarChart, echo=FALSE}
facultyAndStaffWithNAFiltered$Loan.Month.Eng <- factor(facultyAndStaffWithNAFiltered$Loan.Month.Eng,levels = c("January", "February", "March", "April", "May", "June", "July", "August", "September", "October", "November", "December"))

p <- ggplot(data = facultyAndStaffWithNAFiltered, aes(x = Loan.Month.Eng, fill = New.Patron.Group)) + geom_bar(position = 'dodge') + theme_minimal() + labs(x = "Loan Month", y = "Number of Items Loaned", title = "Loan Month by Patron Group") + theme(axis.text.x = element_text(size = 6, angle = 90), axis.title.y = element_text(size = 8), axis.title.x = element_text(size = 8), title = element_text(size = 9)) + scale_fill_discrete(name = "Patron Group") + theme(legend.text = element_text(size = 6), legend.title = element_text(size = 8))

ggplotly(p)
```

#### *Return Month*
###### Return Month Ranking (Most frequent to least):
```{r facultyReturnMonthFreqTable, eval=FALSE, echo=FALSE}
freq(CMUFacultyData$Return.Month.Eng, sort = "dec", total = TRUE)

freq(CMUStaffData$Return.Month.Eng, sort = "dec", total = TRUE)
```
Ranking | Carnegie Mellon Staff | Carnegie Mellon Faculty
------------- | ------------- | ------------- 
 1  | September | January
 2  | October | May
 3  | January | December
 4  | June | September
 5  | March | April
 6  | August | July
 7  | November | October
 8  | April | March
 9  | July | February
 10 | December | August
 11 | February | November
 12 | May | June
 
###### Bar Graph and Distribution Shape:
```{r facultyReturnDateBarChart, echo=FALSE}
facultyAndStaffWithNAFiltered$Return.Month.Eng <- factor(facultyAndStaffWithNAFiltered$Return.Month.Eng,levels = c("January", "February", "March", "April", "May", "June", "July", "August", "September", "October", "November", "December"))

p <- ggplot(data = facultyAndStaffWithNAFiltered, aes(x = Return.Month.Eng, fill = New.Patron.Group)) + geom_bar(position = 'dodge') + theme_minimal() + labs(x = "Return Month", y = "Number of Items Loaned", title = "Return Month by Patron Group") + theme(axis.text.x = element_text(size = 6, angle = 90), axis.title.y = element_text(size = 8), axis.title.x = element_text(size = 8), title = element_text(size = 9)) + scale_fill_discrete(name = "Patron Group") + theme(legend.text = element_text(size = 6), legend.title = element_text(size = 8))

ggplotly(p)
```

#### *Loan Hour*
###### Loan Hour Frequency Table for Faculty:
```{r facultyLoanHourFreqTable, echo=FALSE}
freq(CMUFacultyData$Loan.Hour.Read, sort = "dec", total = TRUE)
```

###### Loan Hour Frequency Table for Staff:
```{r staffLoanHourFreqTable, echo=FALSE}
freq(CMUStaffData$Loan.Hour.Read, sort = "dec", total = TRUE)
freq(CMUStudentData$Loan.Hour.Read, sort = "dec", total = TRUE)
```

###### Bar Graph and Distribution Shape:
```{r facultyLoanHourBarChart, echo=FALSE}
facultyAndStaffAndStudentWithNAFiltered <- filter(newdata, newdata$New.Patron.Group == "Staff" | newdata$New.Patron.Group == "Faculty" | newdata$New.Patron.Group == "Student")

facultyAndStaffAndStudentWithNAFiltered$Loan.Hour.Read <- factor(facultyAndStaffAndStudentWithNAFiltered$Loan.Hour.Read, levels = c("12AM", "1AM", "2AM", "3AM", "4AM", "5AM", "6AM", "7AM", "8AM", "9AM", "10AM", "11AM", "12PM", "1PM", "2PM", "3PM", "4PM", "5PM", "6PM", "7PM", "8PM", "9PM", "10PM", "11PM"))

p <- ggplot(data = facultyAndStaffAndStudentWithNAFiltered, aes(x = Loan.Hour.Read, fill = New.Patron.Group)) + geom_bar(position = 'dodge') + theme_minimal() + labs(x = "Loan Hour", y = "Number of Items Loaned", title = "Loan Hour by Patron Group") + theme(axis.text.x = element_text(size = 6, angle = 90), axis.title.y = element_text(size = 8), axis.title.x = element_text(size = 8), title = element_text(size = 9)) + scale_fill_discrete(name = "Patron Group") + theme(legend.text = element_text(size = 6), legend.title = element_text(size = 8))

ggplotly(p)

f <- filter(newdata, newdata$New.Patron.Group == "Staff" & newdata$Library.Name == "Hunt Library" | newdata$New.Patron.Group == "Faculty" & newdata$Library.Name == "Hunt Library"  | newdata$New.Patron.Group == "Student" & newdata$Library.Name == "Hunt Library")

f$Loan.Hour.Read <- factor(f$Loan.Hour.Read, levels = c("12AM", "1AM", "2AM", "3AM", "4AM", "5AM", "6AM", "7AM", "8AM", "9AM", "10AM", "11AM", "12PM", "1PM", "2PM", "3PM", "4PM", "5PM", "6PM", "7PM", "8PM", "9PM", "10PM", "11PM"))

f <- ggplot(data = f, aes(x = Loan.Hour.Read, fill = New.Patron.Group)) + geom_bar(position = 'dodge') + theme_minimal() + labs(x = "Loan Hour", y = "Number of Items Loaned", title = "Loan Hour by Patron Group (Hunt Library)") + theme(axis.text.x = element_text(size = 6, angle = 90), axis.title.y = element_text(size = 8), axis.title.x = element_text(size = 8), title = element_text(size = 9)) + scale_fill_discrete(name = "Patron Group") + theme(legend.text = element_text(size = 6), legend.title = element_text(size = 8))

ggplotly(f)

f <- filter(newdata, newdata$New.Patron.Group == "Staff" & newdata$Library.Name == "Engineering & Science Library" | newdata$New.Patron.Group == "Faculty" & newdata$Library.Name == "Engineering & Science Library"  | newdata$New.Patron.Group == "Student" & newdata$Library.Name == "Engineering & Science Library")

f$Loan.Hour.Read <- factor(f$Loan.Hour.Read, levels = c("12AM", "1AM", "2AM", "3AM", "4AM", "5AM", "6AM", "7AM", "8AM", "9AM", "10AM", "11AM", "12PM", "1PM", "2PM", "3PM", "4PM", "5PM", "6PM", "7PM", "8PM", "9PM", "10PM", "11PM"))

f <- ggplot(data = f, aes(x = Loan.Hour.Read, fill = New.Patron.Group)) + geom_bar(position = 'dodge') + theme_minimal() + labs(x = "Loan Hour", y = "Number of Items Loaned", title = "Loan Hour by Patron Group (Sorrells)") + theme(axis.text.x = element_text(size = 6, angle = 90), axis.title.y = element_text(size = 8), axis.title.x = element_text(size = 8), title = element_text(size = 9)) + scale_fill_discrete(name = "Patron Group") + theme(legend.text = element_text(size = 6), legend.title = element_text(size = 8))

ggplotly(f)
```

### Categorical Variables  

#### *Material Type*
###### Material Type Ranking (Top 5):
```{r CMUFacultyMaterialTypeFreqTable, eval=FALSE, echo=FALSE}
freq(CMUFacultyData$Material.Type, sort = "dec", total = TRUE)

freq(CMUStaffData$Material.Type, sort = "dec", total = TRUE)
```
Ranking | Carnegie Mellon Staff | Carnegie Mellon Faculty
------------- | ------------- | ------------- 
 1  | Book | Book
 2  | Equipment | Video Recording
 3  | Video Recording | Music Score
 4  | Music Score | Other
 5  | iPad | Equipment


###### Bar Graph:
```{r CMUFacultyMaterialTypeBarChart, echo=FALSE}
p <- ggplot(data = facultyAndStaffWithNAFiltered, aes(x = Material.Type, fill = New.Patron.Group)) + geom_bar(position = 'dodge') + theme_minimal() + labs(x = "Material Type", y = "Number of Items Loaned", title = "Types of Material Loaned by Patron Group") + theme(axis.text.x = element_text(size = 6, angle = 90), axis.title.y = element_text(size = 8), axis.title.x = element_text(size = 8), title = element_text(size = 9)) + scale_fill_discrete(name = "Patron Group") + theme(legend.text = element_text(size = 6), legend.title = element_text(size = 8))

#ggplotly(p)

p <- ggplot(data = facultyAndStaffWithNAFiltered, aes(x = Material.Type, fill = New.Patron.Group)) + geom_bar(position = 'fill') + theme_minimal() + labs(x = "Material Type", y = "Proportion of Items Loaned", title = "Types of Material Loaned by Patron Group") + theme(axis.text.x = element_text(size = 6, angle = 90), axis.title.y = element_text(size = 8), axis.title.x = element_text(size = 8), title = element_text(size = 9)) + scale_fill_discrete(name = "Patron Group") + theme(legend.text = element_text(size = 6), legend.title = element_text(size = 8))

ggplotly(p)
```

#### *Subject*
###### Top 25 Most Common Words For Faculty (Not in Order):
```{r wordCorpusFaculty, include=FALSE}
wordCorpus <- Corpus(VectorSource(CMUFacultyData$Subjects))

wordCorpus <- tm_map(wordCorpus, content_transformer(tolower))

wordCorpus <- tm_map(wordCorpus, removeWords, stopwords("english"))

#wordCorpus <- tm_map(wordCorpus, stripWhitespace)

wordCorpus <- tm_map(wordCorpus, removeNumbers)

wordCorpus <- tm_map(wordCorpus, removePunctuation)

wordCorpus <- tm_map(wordCorpus, removeWords, c("etc", "stateshistory", "aspects", "york", "conditions", "modernth", "stateshistoryth")) 

dtm <- TermDocumentMatrix(wordCorpus)
#as.matrix(dtm)
findFreqTerms(dtm,167)
```
Words|               |               |               |
------------- | ------------- | ------------- | ------------- | -------------  
**Art** | **Century** | **Social** | Language | **States**     
Women | **Literature** | Relations | **History** | **United**
**Criticism** | Political | **African** | **Films** | Interpretation
**War** | **World** | **Motion** | **Music** | Government
**American** | **English** | **Feature** | **Architecture** | **Theory**

###### Top 25 Most Common Words For Staff (Not in Order):
```{r wordCorpusStaff, include=FALSE}
wordCorpus <- Corpus(VectorSource(CMUStaffData$Subjects))

wordCorpus <- tm_map(wordCorpus, content_transformer(tolower))

wordCorpus <- tm_map(wordCorpus, removeWords, stopwords("english"))

#wordCorpus <- tm_map(wordCorpus, stripWhitespace)

wordCorpus <- tm_map(wordCorpus, removeNumbers)

wordCorpus <- tm_map(wordCorpus, removePunctuation)

wordCorpus <- tm_map(wordCorpus, removeWords, c("etc", "stateshistory", "aspects", "york", "conditions", "modernth", "stateshistoryth")) 

dtm <- TermDocumentMatrix(wordCorpus)
#as.matrix(dtm)
findFreqTerms(dtm,146)
```
Words|               |               |               |
------------- | ------------- | ------------- | ------------- | -------------  
**Social** | **Theory** | Computer | Works | **Century**
**English** | Science | **Architecture** | **States** | **American**
**Literature** | **United** | **Art** | **Criticism** | **History**
**World** | Photography | **War** | **African** | **Motion**
**Films** | **Feature** | **Music** | Piano | Fiction

*Bolded words are words that appears in both top words for faculty and staff  


#### *Library*
###### Library Ranking (Top 5, most visited to least):
```{r CMUFacultyLibraryFreqTable, eval=FALSE, echo=FALSE}
freq(CMUFacultyData$Library.Name, sort = "dec", total = TRUE)

freq(CMUStaffData$Library.Name, sort = "dec", total = TRUE)
```

Ranking | Carnegie Mellon Staff | Carnegie Mellon Faculty
------------- | ------------- | ------------- 
 1  | Hunt Library | Hunt Library
 2  | Engineering & Science Library | Engineering & Science Library
 3  | Offsite Repository | Qatar Library
 4  | Mellon Institute Library | Mellon Institute Library
 5  | Qatar Library | Offsite Repository


###### Bar Graph:
```{r CMUFacultyLibraryBarGraph, echo=FALSE}
p <- ggplot(data = facultyAndStaffWithNAFiltered, aes(x = Library.Name, fill = New.Patron.Group)) + geom_bar(position = 'dodge') + theme_minimal() + labs(x = "Library", y = "log(Number of Items Loaned)", title = "Number of Items Loaned by Library") + theme(axis.text.x = element_text(size = 6, angle = 90), axis.title.y = element_text(size = 8), axis.title.x = element_text(size = 8), title = element_text(size = 9)) + scale_fill_discrete(name = "Library") + theme(legend.text = element_text(size = 6), legend.title = element_text(size = 8)) + scale_y_continuous(trans = 'log')

ggplotly(p)
```

#### *Publisher*
###### Ranking of Publishers (Top 10, excluding N/A):
```{r CMUFacultyPublisherFreqTable, eval=FALSE, echo=FALSE}
freq(CMUFacultyData$Publisher, sort = "dec", total = TRUE)

freq(CMUStaffData$Publisher, sort = "dec", total = TRUE)
```

Ranking | Carnegie Mellon Staff | Number | Carnegie Mellon Faculty | Number |
------------- | ------------- | ------------- | ------------- | -------------
1 | **Oxford University Press** | 177 | **Cambridge University Press** | 307
2 | **Cambridge University Press** | 174 | **Oxford University Press** | 303
3 | Chadwyck-Healey | 130 |**Routledge** | 157
4 | **Routledge** | 76 | **Princeton University Press** | 114
5 | Library of Congress Photoduplication Service | 64 | Palgrave Macmillan | 97
6 | Wiley | 61 | University of Chicago Press | 90
7 | MIT Press | 59 | **Yale University Press** | 85
8 | **Springer** | 55 | **Springer** | 83
9 | **Yale University Press** | 53 | Harvard University Press | 82
10 | **Princeton University Press** | 47 | University of California Press | 80


#### *Publication Date*
###### Ranking of Time Period (Top 5, excluding NA):
```{r CMUFacultyPubDateFreqTable, eval=FALSE, echo=FALSE}
freq(dateAndFacultyTable$New.Publication.Date, sort = "dec", total = TRUE)

dateAndStaffTable <- filter(newdata, newdata$New.Publication.Date != "NA" & newdata$New.Patron.Group == "Staff")

freq(dateAndStaffTable$New.Publication.Date, sort = "dec", total = TRUE)
```
Ranking | Carnegie Mellon Staff | Carnegie Mellon Faculty
------------- | ------------- | ------------- 
1 | 2010-2014 | 2010-2014
2 | 2000-2004 | 2015-2019
3 | 2015-2019 | 2005-2009
4 | 2005-2009 | 2000-2004
5 | 1995-1999 | 1995-1999

###### Bar Graph (Excluding NA):
```{r CMUFacultyPubDateBarGraph, echo=FALSE}
facultyAndStaffWithNAFiltered <- filter(newdata, newdata$New.Patron.Group == "Staff" | newdata$New.Patron.Group == "Faculty")

naDateFiltered <- filter(facultyAndStaffWithNAFiltered, facultyAndStaffWithNAFiltered$New.Publication.Date != "NA")

p <- ggplot(data = naDateFiltered, aes(x = New.Publication.Date, fill = New.Patron.Group)) + geom_bar(position = 'dodge') + theme_minimal() + labs(x = "Publication Date", y = "Frequency", title = "Frequency of Publication Date (CMU Faculty)") + theme(axis.title.y = element_text(size = 8), axis.title.x = element_text(size = 8), title = element_text(size = 9), axis.text.x = element_text(angle = 90, size = 5)) + scale_fill_discrete(name = "Patron Group")

ggplotly(p)
```

###### Boxplot of Book Age (After Square Root Transformation):
```{r CMUFacultyBookAgeBoxplot, echo=FALSE}
naDateFiltered$Book.Age.SqrtTransform <- (as.numeric(naDateFiltered$Book.Age.SqrtTransform))

ggplot(data = naDateFiltered, aes(x = Book.Age.SqrtTransform, fill = New.Patron.Group)) + geom_boxplot() + theme_minimal() + labs(x = "sqrt(Book Age)", y = "Frequency", title = " Distribution of Book Age") + theme(axis.text.x = element_text(size = 6), axis.title.y = element_text(size = 8), axis.title.x = element_text(size = 8), title = element_text(size = 9)) + scale_fill_discrete(name = "Patron Group") + theme(legend.text = element_text(size = 6), legend.title = element_text(size = 8))

```

###### Two Sample T-test:
Having summarized the variable, we now turn to the formal hypotheses, we will test if the mean of square root transformation of book age differs significantly for faculty vs. staff: 

$H0: μS-μF = 0$  
$Ha: μS-μF ≠ 0$  

(where $μS$ represent the true mean book age of books borrowed by staff, and $μF$ represent the true mean book age of books borrowed by faculty)   

```{r CMUFacultyBookAgeTtest, echo=FALSE}
t.test(Book.Age.SqrtTransform~New.Patron.Group, data=naDateFiltered)
```
Running a Two Sample t-test yields a test statistic of 1.0457 and a p-value of 0.2957. Since the p-value is greater than the alpha significance level of 0.05, we do not reject the null hypothesis and hence **do not find evidence of a relationship** between book age and patron group

